Total Platform Cyber Protection

### 2016-05-31 paper.tex
finished proof-reading till 5.1

Due to the hardware-specific nature of firmware, \emph{reverse
  engineering} is critical to understanding the firmware. In addition,
reverse engineering is particularly difficult because source code is
frequently unavailable, and vendors desire to protect their
intellectual property makes them actively obfuscate their
firmware. All this means that, extracting semantically useful
information from firmware is a key first step to performing any
security analysis of the firmware.

@@

Finally, even if we find vulnerabilities or Trojan logic in a
firmware, there is still the unanswered questions of how to patch or
update the functionality of the firmware while still guaranteeing the
behavior of the firmware. This is particularly complicated due to the
real-time requirements of the firmware and the potentially concurrent
executions.

>>>>

Due to the hardware-specific nature of firmware, \emph{reverse
  engineering} is critical to understanding the firmware. In addition,
reverse engineering is particularly challenging because source code is
frequently unavailable, and vendors' desire to protect their
intellectual property makes them actively obfuscate their
firmware. All this means that, extracting semantically useful
information from firmware is a key first step to performing any
security analysis of the firmware.

@@

Finally, even if we find vulnerabilities or Trojan logic in a
firmware, there is still the unanswered question of how to patch or
update the functionality of the firmware while still guaranteeing the
behavior of the firmware. This is particularly complicated due to the
real-time requirements of the firmware and the potentially concurrent
executions.
